---
title: "ML Iris Dataset"
author: "Michael Harrison"
date: "May 1, 2017"
output: html_document
---

# 1. Prepare Problem
# a) Load packages
```{r}
library(caret)
library(caretEnsemble)
library(ggplot2)
library(lattice)
```

# b) Load dataset
```{r}
data("iris")
dataset <- iris
```

# c) Split-out validation dataset
```{r}
inTrain <- createDataPartition(iris$Species, p=.7, list=FALSE)
training <- iris[inTrain,]
testing <- iris[-inTrain,]
```


# 2. Summarize Data
# a) Descriptive statistics
```{r}
head(training, 6)
```
```{r}
dim(training)
```
```{r}
summary(training)
```
```{r}
sapply(training[,1:4], sd)
```
```{r}
cor(training[,1:4])
```

# b) Data visualizations
```{r}

```



# 3. Prepare Data
# a) Data Cleaning
# b) Feature Selection
# c) Data Transforms

# 4. Evaluate Algorithms
# a) Test options and evaluation metric
# b) Spot-Check Algorithms
# c) Compare Algorithms

# 5. Improve Accuracy
# a) Algorithm Tuning
# b) Ensembles

# 6. Finalize Model
# a) Predictions on validation dataset
# b) Create standalone model on entire training dataset
# c) Save model for later use